\documentclass{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
\usepackage{booktabs}
\usepackage{aicid}

\title{The \textsf{aicid} package}
\author{Michele Renda}
\date{Version 0.0.4 \\ 2026-06-18}

\begin{document}
\maketitle

\section{Purpose}

The \textsf{aicid} package provides small profile links for AICID
identifiers in LaTeX documents. It is intended for author blocks,
acknowledgements, contributor lists, and similar places where an AI
collaborator or AI scientific agent should be linked to a public AICID
profile.

The package is deliberately small. It depends on \textsf{graphicx} and uses
\textsf{hyperref} when that package is loaded. If \textsf{hyperref} is not
loaded, the icon and identifier commands still typeset normally, but without
links.

\section{Installation}

For a single manuscript, place the following files next to the main
\texttt{.tex} file:

\begin{itemize}
\item \texttt{aicid.sty}
\item \texttt{aicid-logo.pdf}
\end{itemize}

Then load the package in the preamble:

\begin{verbatim}
\usepackage{hyperref}
\usepackage{aicid}
\end{verbatim}

\section{User commands}

\begin{center}
\begin{tabular}{ll}
\toprule
Command & Meaning \\
\midrule
\verb|\aicid{<AICID>}| & Print a linked AICID icon. \\
\verb|\aicidfull{<AICID>}| & Print a linked icon followed by the identifier. \\
\verb|\aicidid{<AICID>}| & Print the linked identifier text without the icon. \\
\verb|\aicidauthor{<name>}{<AICID>}| & Print a name followed by a linked icon. \\
\verb|\aicidsetheight{<dim>}| & Set the icon height. \\
\verb|\aicidsetbaseurl{<url>}| & Override the profile base URL. \\
\bottomrule
\end{tabular}
\end{center}

The default icon height is \texttt{1.75ex}. The default profile base URL is:

\begin{verbatim}
https://aicid.net/agents/
\end{verbatim}

\section{Examples}

An acknowledgement entry can be written as:

\begin{verbatim}
Poe Ledger\aicid{AICID-8852-3802-2226-1236}
\end{verbatim}

which renders as:

\medskip

Poe Ledger\aicid{AICID-8852-3802-2226-1236}

\medskip

To show the identifier explicitly:

\begin{verbatim}
\aicidfull{AICID-8852-3802-2226-1236}
\end{verbatim}

which renders as:

\medskip

\aicidfull{AICID-8852-3802-2226-1236}

\medskip

For author-like lists, use:

\begin{verbatim}
\aicidauthor{Poe Ledger}{AICID-8852-3802-2226-1236}
\end{verbatim}

which renders as:

\medskip

\aicidauthor{Poe Ledger}{AICID-8852-3802-2226-1236}

\section{License}

Copyright \textcopyright{} 2026 Michele Renda.

This work may be distributed and/or modified under the conditions of the
LaTeX Project Public License, either version 1.3c of this license or (at your
option) any later version.

This work has the LPPL maintenance status ``maintained''. The Current
Maintainer of this work is Michele Renda.

\end{document}
